Conditions for successful wetting during collision between emulsion droplets and curved substrate

### 2012-10-04 Text/paper mc edit.tex
my edit of the text file

\title{Conditions for successful wetting during collision between emulsion droplets and curved substrate}
\begin{document}
\maketitle

@@

\section{Boundary conditions}
There are a number of boundary conditions in the lattice Botlzmann system, as bounce-back \cite{yu}, Zou-He pressure and velocity boundary conditions \cite{zouhe-boundary}, Inamuro boundary conditions \cite{inamuro-scalar-boundary}. The lattice Boltzmann model operates with discrete populations and on the rectangular grid. That brings certain challenges to match boundary conditions imposed on the macroscopic variables to the discrete populations world.

@@

The suggested algorithm uses the mirror boundary conditions. Figure \ref{fig:free:surface} shows the staircase approximation of the curved boundaries. 
Thus, the normal to the boundary is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}.  Imposing the
symmetric boundary conditions requires $\phi_{n,F}$=$\phi_{n,B}+\partial_{\perp} \phi$. For any solid boundary nodes, the normal to the staircase approximation was calculated and the phase value was assigned according to the latter equation.  In terms of population, to conserve the mass in the phase domain we used the bounce-back condition which conserves the mass \cite{yu}.  
\begin{figure}
\includegraphics[width=\textwidth]{Figures/free_surface.eps}
\caption{Free-surface boundary condition represented in the lattice Boltzmann method. 
Boundary nodes are depicted by crosses, and fluid nodes are represented by dots. One imposes only phase values at the nodes to calculate laplacians used in the equilibrium functions. In the population space, one uses the bounce-back rule \cite{yu}, which conserves mass.
\label{fig:free:surface}}
\end{figure}
\begin{figure}
\includegraphics[width=0.5\textwidth]{Figures/droplet_shapes_curved_substrates.eps}
\includegraphics[width=0.5\textwidth]{Figures/main_curve_circle.eps}\\
\caption{Equilibrium angles at the curved substrate. One can see that the contact angle at the curved substrate mimics the analytically calculated contact angle at the flat substrate. \label{fig:equilibrium:droplet:curved}}
\end{figure}

>>>>

\title{Conditions for successful wetting during collision between emulsion droplets and curved substrate}
\begin{document}
\maketitle
\section{Abstract}
\section{introduction}
Emulsion droplets are often used a delivery vehicle to deposit active ingredients on target substrates in application such as drug delivery, cosmetics and detergent products. In order to fulfill their function emulsion formulation are optimized in terms of emulsion droplets size, stability, surface properties and interaction forces with the target substrate. Virtually the properties of the emulsion droplets while stored before their use and their behavior after wetting the target substrate can be finely designed using well established physical models that identify the critical parameters controlling stability and adhesion properties.

However, to fulfill its function, the emulsion droplets need to be successfully transferred on the substrate. This transfer process, that involves the complex sequence of events that take the emulsion droplets from the formulated state to the substrate is not as well characterized and the role of the different parameters related to the emulsion, substrate and hydrodynamic interaction mediated by the continuous phase is still poorly defined. Recent AFM studied of emulsion interactions identified the critical role of hydrodynamic effect on the repulsion between two emulsions colliding at different speed. The effective disjointing pressure preventing contact and coalescence between the two emulsion droplets has an electrostatic and an hydrodynamic component. This suggest that also during the process of emulsion collision on a substrate successful contact and wetting of the surface critically depend on the interplay of the hydrodynamic and inter-facial properties.

In this work we use Lattice Boltzmann simulation methods to study the effect of inter-facial and hydrodynamic parameters on the efficiency of the wetting process during collision. We simulate a spherical emulsion droplets colliding on a curved "cylindrical" substrate. The properties of the substrate are set by controlling its curvature and the three phase contact angle with the emulsion droplet and the surrounding fluid. The emulsion droplet is characterized by its size, viscosity and inter-facial tension with the surrounding fluid. The hydrodynamic properties are explored by simulating droplet collision on the substrate under different flow conditions.

In the Next section we describe the idealized collision system simulated, the physical properties controlled in the simulation and the range of parameters explored (parameter space). In the following section we provide details about the simulation methods and its validation against other methodology previously proposed (Binary-liquid lattice Boltzmann model). Next we summarize the results of the parametric study focusing on the behavior of the emulsion as it collides with the substrate as a function of the interfacial and hydrodinamic parameters explored (Results). We then propose a map of the deposition efficiency within the explored parametric space (deposition efficiency map). Finally we summarize the results and relate to the related application areas (conclusions).

\section{parameter space}

@@

\subsection{Boundary conditions}
There are a number of boundary conditions in the lattice Botlzmann system, as bounce-back \cite{yu}, Zou-He pressure and velocity boundary conditions \cite{zouhe-boundary}, Inamuro boundary conditions \cite{inamuro-scalar-boundary}. The lattice Boltzmann model operates with discrete populations and on the rectangular grid. That brings certain challenges to match boundary conditions imposed on the macroscopic variables to the discrete populations world.

@@

The suggested algorithm uses the mirror boundary conditions. Figure \ref{fig:free:surface} shows the staircase approximation of the curved boundaries. 
Thus, the normal to the boundary is always located by the angle of multiple of $45$ degrees, see Fig. \ref{fig:free:surface}.  Imposing the
symmetric boundary conditions requires $\phi_{n,F}$=$\phi_{n,B}+\partial_{\perp} \phi$. For any solid boundary nodes, the normal to the staircase approximation was calculated and the phase value was assigned according to the latter equation.  In terms of population, to conserve the mass in the phase domain we used the bounce-back condition which conserves the mass \cite{yu}.

%\begin{figure}
%\includegraphics[width=\textwidth]{Figures/free_surface.eps}
%\caption{Free-surface boundary condition represented in the lattice Boltzmann method. 
%Boundary nodes are depicted by crosses, and fluid nodes are represented by dots. One imposes only %phase values at the nodes to calculate laplacians used in the equilibrium functions. In the %population space, one uses the bounce-back rule \cite{yu}, which conserves mass.
%\label{fig:free:surface}}
%\end{figure}

%\begin{figure}
%\includegraphics[width=0.5\textwidth]{Figures/droplet_shapes_curved_substrates.eps}
%\includegraphics[width=0.5\textwidth]{Figures/main_curve_circle.eps}\\
%\caption{Equilibrium angles at the curved substrate. One can see that the contact angle at the %curved substrate mimics the analytically calculated contact angle at the flat substrate. %\label{fig:equilibrium:droplet:curved}}
%\end{figure}

\section{Results}

\section{Deposition efficiency map}
